---
title: "Data Mining Part 2"
author: "Veerasak Kritsanapraphan"
date: "4/6/2017"
output:
  ioslides_presentation: default
  beamer_presentation: default
  slidy_presentation: default
---
<style>
.title-slide {
  background-color: #DB598A; /* #EDE0CF; ; #CA9F9D*/
}

.title-slide hgroup > h1{
 font-family: 'Oswald', 'Helvetica', sanserif; 
}

.title-slide hgroup > h1, 
.title-slide hgroup > h2,
.title-slide hgroup > p {
  color: #FFFFFF ;  
}
</style>

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = FALSE)
opts_chunk$set(warning=FALSE, message=FALSE)
opts_chunk$set(tidy.opts=list(width.cutoff=58),tidy=TRUE)
```

## Prediction Model Performance

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Prepare Data

```{r}
# Prepare iris
set.seed(567)
ind <- sample(2, nrow(iris), replace=TRUE, prob=c(0.7, 0.3))
traindata <- iris[ind==1,]
testdata <- iris[ind==2,]
```

## Create Decision Tree Model
```{r}
library(party)

myFormula <- Species ~ Sepal.Length + Sepal.Width + Petal.Length + Petal.Width
iris_ctree <- ctree(myFormula, data=traindata)
```

## Create Confusion Matrix from Training Data
```{r}
library(caret)
trainPred = predict(iris_ctree,traindata)
confusionMatrix(traindata$Species,trainPred)
```

